---
title: "My Fancy Slide"
author: "Partha S. Ghose"
date: "4/9/2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## My First Slide

```{r, comment="", echo = TRUE}
head(mtcars)
```



## The Bulleted Slide
**Displaying a plot**

- *Creating a simple slide*
```{r, echo = TRUE}
plot(mtcars$wt,mtcars$mpg, xlab = "Weight", ylab = "Milage")
```

#### Ordered Lists
1. Item 1
2. Item 2


## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

